A Vignetted View of Computer Science through Citation Analysis

### 2019-12-17 Scientometrics/comp.tex
added new figure to latex

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{quad-chart-narrow.pdf}
\caption{Co-citation analysis.
(a) The variable-level clustering technique (adapted from
Small and Sweeney (1985)).
(b) The distribution of publications (using fractional counting)
across four main categories.
(c) The Venn diagram of the fractional counting given in (b).
(d) The distribution of cluster sizes (logarithmic y-axis) as
a function of the number of iterations of the agglomerative
clustering technique; note that the largest cluster is
extremely large when the number of iterations exceeds 600.
}
\label{fig:quad-chart}
\end{figure}
